Sample variance in weak lensing: how many simulations are required?

### 2016-01-08 Paper/paper.tex
very minor change
Zoltan edits

\newcommand{\bb}[1]{\mathbf{#1}}
\newcommand{\bbh}[1]{\mathbf{\hat{#1}}}
\newcommand{\h}[1]{\hat{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{Simulating cosmic variance in Weak Lensing: effects on parameter inferences}

@@

Constraining cosmology using Weak Gravitational Lensing consists in comparing measured feature vectors, of various dimensions $N_b$, with simulated ones. An accurate estimate of the $N_b\times N_b$ feature covariance matrix is essential to obtain accurate parameter confidence intervals. When this covariance matrix $\bb{C}$ is measured from simulations, an important question to ask is how big the simulation set should be for an accurate estimation of $\bb{C}$. We construct different mock ensembles with $N_r$ realizations of the same shear field, using a common randomization procedure based on $N_s<N_r$ independent $N$--body simulations. Previous work \citep{DodelsonSchneider13} showed that noise fluctuations in the feature covariance lead, at quadratic order, to a $O(1/N_r)$ degradation of parameter constraints. Using a variety of features that include shear-shear power spectra and peak counts, we show that cubic and quartic covariance fluctuations lead to additional $O(1/N_r^2)$ error degradation that is not negligible when $N_r$ is only a factor of a few bigger than $N_b$. When we study the large $N_r$ limit we find that a single $N$--body simulation can be recycled a large number of times to produce an ensemble of $N_r=10^5$ shear realizations that are mutually independent. We also find that a small number of independent $N$--body simulations (1 or 2) are necessary to forecast parameter error bars at percent accuracy, while a larger number might be needed to measure accurate feature ensemble means.

\end{abstract}

@@

\section{Introduction}
%
Weak Gravitational lensing is a promising cosmological probe for constraining the Dark Energy equation of state $w$, and has been considered by a range of past (CFHTLens \citep{cfht1,cfht2}), current (DES \citep{DES}) and future (LSST \citep{LSST}) experiments. In an era where cosmology is becoming data driven, accurate numerical simulations of shear fields are becoming important for a number of reasons including the study of baryonic effects \citep{BaryonXiuyuan}, non--Gaussian statistics \citep{PeaksJan,MinkJan,MinkPetri} and various systematics. Building cosmological predictions from simulations naturally introduces fluctuations in the forecasts, mainly due to cosmic variance. These fluctuations have been shown to have non negligible effects on estimates of features covariance matrices and hence on parameter constraints (see \citep{DodelsonSchneider13}). This work studies this issue further, focusing on the number of independent $N$--body simulations that is necessary to run for obtaining accurate estimates of parameter constraints, with particular focus on $w$. This paper is organized as follows: in the first paragraph we briefly describe the shear simulation methods we used, as well as the formalism we adopted to compute cosmological parameter constraints. We then outline our main findings and discuss the results, as well as future prospects for continuing this study.

@@

\subsection{Shear field simulations}
\label{shearsim}
%
In this paragraph we describe how we constructed our shear field ensembles. Background galaxies at redshift $z_s$ are lensed by large scale structure between $z=0$ and $z_s$. The shape distortions due to the cosmic shear $\pmb{\gamma}$ can be computed in terms of the dark matter gravitational potential $\Phi(\bb{x},z)$. Because the evolution of $\Phi$ in redshift is non--linear, its evolution needs to be computed with numerical simulations. We make use of the public code \texttt{Gadget2} \citep{Gadget2}, with which we run a sequence of dark--matter--only $N$--body simulations that track the evolution of the density fluctuations in the large scale structure of the universe. We assume a standard $\Lambda$CDM framework with $(\Omega_m,\Omega_\Lambda,h,w,\sigma_8,n_s)=(0.26,0.74,0.72,-1,0.8,0.96)$ and we fix the comoving size of the simulation box to $240\mathrm{Mpc}/h$. We fill the box with $512^3$ particles, which correspond to a mass resolution of $10^{10}M_\odot$. We assume a uniform galaxy distribution at a constant redshift $z_s=2$ (at which the simulation box has an angular size of $\theta_{box}=3.5\mathrm{deg}$) and we discretize the mass distribution between $z_s$ and the observer at $z=0$ with a sequence of 46 two dimensional lenses of thickness $80\mathrm{Mpc}/h$. The surface density on each lens is computed by projecting the three dimensional density measured from \texttt{Gadget2} snapshots. We then apply the multi--lens--plane algorithm (see \citep{RayTracingHartlap,RayTracingJain} for example) to trace the deflections of $n_{ray}^2=2048^2$ light rays arranged on a square grid of total size $\theta_{box}$, from $z=0$ to $z_s$. The light deflection calculations have been performed with our implementation of multi--lens--plane algorithm, which is part of the \texttt{LensTools} computing package \citep{LensTools} (released under the \texttt{MIT} license). Different realizations $r$ of the same shear field $\pmb{\gamma}_r(\pmb{\theta})$ can be generated with different choices of the lenses that lay between the observer and $z_s$. The randomization procedure we adopt is the following:

\begin{itemize}
\item Pick a lens redshift $z_l$, and select the snapshot at $z_l$ from the $i$--th $N$--body simulation at disposal, where $i$ is a random number in $[1,N_s]$
\item Choose randomly a direction between the three choices ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$: the lens plane will be pependicular to this direction
\item Choose the cutting point of the plane in the snapshot: because the lens thickness is 1/3 the size of the box, we can cut three different slices of the simulation box for each orientation ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$, which gives a total of 9 choices for generating a lens plane out of a $N$--body snapshot
\item Perform a periodical random shift of the lens plane along its two directions
\item Repeat this procedure for each lens redshift $z_l$  
\end{itemize}  
%
This randomization procedure allows us to produce an arbitrary number $N_r$ of mock shear realizations $\pmb{\gamma}_r(\pmb{\theta})$, which however will not be all independent if $N_s$ is not large enough. Using a set of 200 independent $N$--body simulations, we construct different ensembles with different choices of $N_s\in[1,200]$, each made of 1000 mock shear realizations. We also build an additional ensemble with $N_s=1$ and $10^5$ mocks. From each of these mocks we reconstruct the convergence $\kappa_r(\pmb{\theta})$ and measure its angular power spectrum $P^{\kappa\kappa}_r(l)$ defined as
\begin{equation}
\langle\tilde{\kappa}_r(\bb{l})\tilde{\kappa}_r(\bb{l}')\rangle = (2\pi)^2\delta_D(\bb{l}+\bb{l}')P^{\kappa\kappa}_r(l)
\end{equation}
%
As an additional summary statistic, we consider the counts of local $\kappa$ maxima of a certain height $\kappa_0$, $n_r(\kappa_0)$ (from now on \textit{peak counts}), with varying $\kappa_0$. The fact that the ensemble of $N_r$ mocks is not completely independent if $N_s$ is not large enough can have an effect on the covariance estimators of $P^{\kappa\kappa},n(\kappa_0)$.

\subsection{Parameter inference}
%
Let $\bbh{d}$ a feature of dimension $N_b$, $\bb{d}(\bb{p})$ be the smooth expectation of this feature at a point $\bb{p}$ in parameter space (which has a dimension $N_p$) and $\bb{C}$ be the $N_b\times N_b$ feature covariance matrix. For the purpose of this work $\bb{p}$ is the triplet $(\Omega_m,w,\sigma_8)$ and $\bb{d}$ is one of the features listed in Table \ref{featuretable}. While, in some cases, $d(\bb{p})$ can usually be predicted reasonably accurately by already existing emulators (see \citep{coyote2,Nicaea} for example), the matter is more complicated for covariance matrices. Estimating $\bb{C}$ from simulations involves generating a series of mock realizations $\bbh{d}_r$ with $r=1...N_r$ and estimating the sample covariance $\bbh{C}$

\begin{equation}
\bb{\bar{d}} = \frac{1}{N_r}\sum_{r=1}^{N_r} \bbh{d}_r
\end{equation}

\begin{equation}
\label{covest}
\bbh{C} = \frac{1}{N_r-1}\sum_{r=1}^{N_r} (\bbh{d}_r - \bar{\bb{d}}) (\bbh{d}_r - \bar{\bb{d}})^T
\end{equation}
%
Assuming a normal feature likelihood, together with a flat prior on the parameter space, the parameter posterior distribution $\mathcal{L}(\bb{p}\vert\bbh{d}_{obs})$ given an observed instance of $\bbh{d}$, which we call $\bbh{d}_{obs}$, can be obtained using Bayes theorem
\begin{equation}
\label{posteriorbayes}
-2\log\mathcal{L}(\bb{p}\vert\bbh{d}_{obs}) = (\bbh{d}_{obs}-\bb{d}(\bb{p}))^T\bbh{C}^{-1}(\bbh{d}_{obs}-\bb{d}(\bb{p}))
\end{equation}
%
For the sake of simplicity, we approximate the posterior as a Gaussian around its maximum. This is easily done approximating the simulated feature at first order around a point $\bb{p}_0$ (that ideally is the maximum of (\ref{posteriorbayes}))
\begin{equation}
\bb{d}(\bb{p}) \approx \bb{d}_0 + \bb{d}_0^\prime(\bb{p}-\bb{p}_0) 
\end{equation}
%
To measure the feature derivatives $\bb{d}'_0$ with respect to cosmology, we make use of the public code \texttt{NICAEA} \citep{Nicaea} for the power spectrum, and we use an independent simulation set (that contains mocks at different combinations of $(\Omega_m,w,\sigma_8)$, see Table \ref{simtable}) for the peak counts.

\begin{table}
\begin{center}
\begin{tabular}{c|c|c||c|c}
\toprule
$\Omega_m$ &  $w$ & $\sigma_8$ & $N_s$ & Number of $\kappa$ ensembles \\ \hline \hline
\midrule

0.26 & -1 & 0.8 & $1\div 200$ & 16 \\
0.29 & -1 & 0.8 & 1 & 1 \\
0.26 & -0.8 & 0.8 & 1 & 1 \\
0.26 & -1 & 0.6 & 1 & 1 \\

\bottomrule
\end{tabular}
\end{center}
\caption{Summary table of the shear ensembles used in this work.}
\label{simtable}
\end{table}

We can build the estimator for the posterior maximum $\bbh{p}$, given the observation $\bbh{d}_{obs}$, as follows:
%
\begin{equation}
\label{estimatormean}
\bbh{p} = \bb{p}_0 + \bbh{T}(\bbh{d}_{obs}-\bb{d}_0)
\end{equation}

\begin{equation}
\bbh{T} = (\bb{d}_0'^T\bbh{C}^{-1}\bb{d}_0')^{-1}\bb{d}_0'^T\bbh{C}^{-1}
\end{equation}
%
Because $\bbh{p}$ is estimated using a noisy data instance $\bbh{d}_{obs}$, its estimate will be scattered around the true value $\langle\bbh{p}\rangle_O$. In the following we use the $\langle\rangle_O$ notation for expectation values taken with respect to observations, while we keep the notation $\langle\rangle$ for expectation values taken with respect to the simulations. Defining the \textit{precision matrix} $\bbh{\Psi}=\bbh{C}^{-1}$, we can express the estimator of the observational scatter in $\bbh{p}$

\begin{equation}
\label{estimatorcovariance}
\h{\Sigma}_\bb{p} = \bbh{F}^{-1}\bb{d}_0'^T\bbh{\Psi}\langle(\bbh{d}_{obs}-\bb{d}_0)(\bbh{d}_{obs}-\bb{d}_0)^T\rangle_O\bbh{\Psi}\bb{d}_0'\bbh{F}^{-1}
\end{equation}

\begin{equation}
\label{estimatorfisher}
\bbh{F} = \bb{d}_0'^T\bbh{\Psi}\bb{d}_0'
\end{equation}
%
Where we introduced the Fisher matrix estimator $\bbh{F} = \bb{d}_0'^T\bbh{\Psi}\bb{d}_0'$ and, for simplicity, we assumed $\langle\bbh{d}_{obs}\rangle_O=\bb{d}_0$, so that $\langle(\bbh{d}_{obs}-\bb{d}_0)(\bbh{d}_{obs}-\bb{d}_0)^T\rangle_O=\bb{C}$. 
When we perform an observation $\bbh{d}_{obs}$, the parameter estimate $\bbh{p}$ is a random draw from a probability distribution with variance $\h{\Sigma}_\bb{p}$, which inherits noise from the simulations. The noise in the covariance estimator (\ref{covest}) and its inverse $\bbh{\Psi}$ propagates all the way to the posterior (\ref{posteriorbayes}), the parameter estimate (\ref{estimatormean}) and its variance (\ref{estimatorcovariance}). Following \citep{DodelsonSchneider13,Taylor12,MasumotoWishart} we compute the expectation value of (\ref{estimatorcovariance}) over simulations, $\langle\h{\Sigma}_\bb{p}\rangle$, up to $O(1/N_r^2)$ by expanding (\ref{estimatorcovariance}) to quartic order in the $\bbh{\Psi}$ statistical fluctuations. Indicating the noiseless parameter covariance as $\Sigma_\bb{p}=\bb{F}^{-1}$, the result we get is \footnote{The details of the calculation are given in Appendix A}

\begin{widetext}
\begin{equation}
\label{quarticdegradation}
\langle\h{\Sigma}_\bb{p}\rangle = \Sigma_\bb{p}\left[1+\frac{N_b-N_p}{N_r}+\frac{(N_b-N_p)(N_b-N_p+2)}{N_r^2}\right] + O\left(\frac{1}{N_r^3}\right)
\end{equation}
\end{widetext}
%
Next, we restrict ourselves to the large $N_r$ limit, and we further investigate the behavior of the $O(1/N_r)$ term. We consider three cases \footnote{The details of these calculations are given in Appendix B}:
\begin{enumerate}
\item If the true data covariance $\bb{C}$ is known, the estimator (\ref{estimatorcovariance}) is biased, and the dominant contribution of the bias comes from the second order fluctuations in $\bbh{\Psi}$. Once the expectation values over simulations are taken, the bias sums up to

\begin{equation}
\label{dodelsonscaling}
\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}\left(1+\frac{N_b-N_p}{N_r}\right)
\end{equation}
%
This is the result obtained by \citep{DodelsonSchneider13}.

\item Usually the true covariance is not known, and it is tempting to plug in its estimator $\bbh{C}$, measured from the same simulation set we use to compute $\bbh{\Psi}$. This approach has been used before in the literature (see \citep{MinkPetri,MinkShirasaki} for example). If we do that, and we do not correct for the $\bbh{\Psi}$ bias, the parameter variance will have a contribution from both the second and first order fluctuations in $\bbh{\Psi}$, which now have a non zero expectation value. In this case the bias sums up to 
\begin{equation}
\label{mockscalinguncorrected}
\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}\left(1-\frac{N_b-N_p}{N_r}\right)
\end{equation}

@@

\section{Conclusion}

In this work we examine the effect of $N$--body simulations based shear ensembles on forecasted cosmological constraints. Our main results can be summarized as follows:

>>>>

\newcommand{\bb}[1]{\mathbf{#1}}
\newcommand{\bbh}[1]{\mathbf{\hat{#1}}}
\newcommand{\h}[1]{\hat{#1}}
\newcommand\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
        \raise1pt\hbox{$<$}}}
\newcommand\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
        \raise1pt\hbox{$>$}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%ZH: I changed to more catchy title:
%\title{Simulating sample variance in weak lensing: effects on parameter inferences}
\title{Sample variance in weak lensing: how many simulations are required?}

@@

Constraining cosmology using weak gravitational lensing consists of
comparing a measured feature vector of dimension $N_b$ with its
simulated counterpart. An accurate estimate of the $N_b\times N_b$
feature covariance matrix $\bb{C}$ is essential to obtain accurate
parameter confidence intervals. When $\bb{C}$ is measured from a set
of simulations, an important question is how large this set should
be. To answer this question, we construct different ensembles of $N_r$
realizations of the shear field, using a common randomization
procedure that recycles the outputs from a smaller number $N_s\leq
N_r$ of independent ray-tracing $N$--body simulations.  We study
parameter confidence intervals as a function of ($N_s,N_r$) in the
range $1\leq N_s\leq 200$ and $1\leq N_r\leq 10^5$.  Previous work
\citep{DodelsonSchneider13} has shown that Gaussian noise in the
feature covariance lead, at quadratic order, to an $O(1/N_r)$
degradation of the parameter confidence intervals. Using a variety of
lensing features measured in our simulations, including shear-shear
power spectra and peak counts, we show that cubic and quartic
covariance fluctuations lead to additional $O(1/N_r^2)$ error
degradation that is not negligible when $N_r$ is only a factor of few
larger than $N_b$. We study the large $N_r$ limit, and find that a
single $N$--body simulation ($N_s=1$) can be repeatedly recycled to
produce as many as $N_r=10^5$ mutually independent shear maps. As a
result, a small number of simulations ($N_b=1$ or $2$) is sufficient
to forecast parameter confidence intervals at percent
accuracy. However, we find that in practice, a larger number of
simulations might be needed to measure accurate feature means and to
avoid parameter biases.
%ZH: I am not sure about the last sentence. I believe it is based on
%    an overly stringent reading of Fig.2, and that in fact we could
%    claim here, instead, that N_s=2 simulations are also sufficient
%    to get the correct mean.
%    See my comments at the end of the Conclusion section. 
\end{abstract}

@@

\section{Introduction}
%
Weak gravitational lensing (WL) is a promising cosmological probe for
constraining the dark energy equation of state $w$, and has been
considered by a range of past (CFHTLens \citep{cfht1,cfht2}),
%ZH: also cite COSMOS survey here...
ongoing (DES \citep{DES}) and future (LSST \citep{LSST})
%ZH: also cite Euclid and WFIRST.
experiments. In an era where cosmology is data driven, accurate
numerical simulations of shear fields are becoming important for
several reasons, including the study of baryonic effects
\citep{BaryonXiuyuan}, 
%ZH: also cite Joop Schaye's hydro-simulation papers on lensing (Semboloni et al), and earlier papers by Martin White et al...  Lloyd Knox et al... and Zentner et al... (I think all of these are in Xiuyuan's paper).
the computation of non--Gaussian statistics
\citep{PeaksJan,MinkJan,MinkPetri} 
%ZH: Add here some citations of other groups - Marian+Bernstein.... Bhuvnesh Jain et al... Refregier et al... Dietrichh+Hartmann... Shirasaki+Yoshida.. (again just copy from our previous papers).
and the  assessment of various systematics.
%ZH: cite papers by Jan+Morgan+Bard... and also Chihway Chan...Shirasaki+Yoshida.. and older ones by Dragan Huterer on photo-z errors..

A fundamental issue with predictions from simulations is that the
finite number of simulations naturally introduces fluctuations in the
forecasts, due to inevitable sample variance~\footnote{Sample variance is a broad term that has been used in the literature to describe a range of phenomena.  Throughout this paper, we use it to refer to the fluctuations in an ensemble of simulations, which represent random realizations of the same initial conditions.}.
%ZH: I think 'cosmic variance' usually refers to observations of the actual sky (which is finite).  
In general, quantities such as the mean or the variance of any feature
(e.g. the shear power spectrum at a multipole $\ell$), measured from a
finite set of simulations, will fluctuate, and can also suffer a bias.
While biases in the estimates of both the mean and the variance have
been studied extensively, the impact of fluctuations in the variance
has received comparatively less attention.  These fluctuations have,
however, been shown to have non-negligible effects on estimates of
features covariance matrices and hence on parameter constraints. In
particular, in the limit of Gaussian fluctuations, the parameter
confidence limits are degraged by a factor
$1+O(1/N_r)$~\citep{DodelsonSchneider13}.
%also cite Taylor Joachimi and Kitching -Morgan

This work studies these issues further, focusing on the number of
independent $N$--body simulations required for an accurate estimate of
the parameter constraints.  Ray-tracing simulations that resolve the
cosmic structures responsible for lensing on arcminute scales are
limited to physical sizes of hundreds of Mpc, and thus cover a solid
angle of only $O(10$ deg$^2)$.  As a result, many simulations are
required to tile a significant fraction of the sky, and to make
predictions for large ``all-sky'' surveys, such as the ones by DES,
LSST, Euclid, WFIRST.  In practice, this has led to the wide-spread
use of ``pseudo-independent'' realizations, i.e. a procedure in which
one randomizes and re-cycles the output of a single 3D simulation
multiple times.
%ZH: Add citations here of papers resorting to this technique
In light of the forthcoming large surveys, it is imperative to assess
the statistical validity of this approach, and to ask how many times a
single simulation can be fairly recycled.  In this paper, we address
these questions with ensembles of up to $N_r=10^5$ random
realizations, extracted from up to $N_s=200$ independent ray-tracing
N-body simulations. We focus in particular on the parameter $w$, and
on two different statistics: the (convergence) power spectrum and
the number counts of peaks.

This paper is organized as follows.  In \S~II, we summarize the shear
simulation methods we utilized, and describe the formalism we adopted
to forecast cosmological parameter constraints. We then vary the
number of simulations and the number of pseudo-independent
realizations, and present our main findings in \S~III. These results
are discussed further in \S~IV.  We offer our conclusions, and suggest
follow-up future work in \S~V.

@@

\subsection{Ray-tracing simulations of the convergence field}
\label{shearsim}
%
In this section, we describe how we constructed our shear field
ensembles. Background galaxies at redshift $z_s$ are lensed by large
scale structures between $z=0$ and $z_s$. The shape distortions due to
the cosmic shear $\pmb{\gamma}$ can be computed in terms of the dark
matter gravitational potential $\Phi(\bb{x},z)$. Because the evolution
of $\Phi$ with redshift is non--linear, it needs to be computed with
numerical simulations. We make use of the public code \texttt{Gadget2}
\citep{Gadget2}, with which we run a sequence of $200$ independent
dark--matter--only $N$--body simulations that track the evolution of
the density fluctuations. We assume a standard $\Lambda$CDM background
universe with the parameters
$(\Omega_m,\Omega_\Lambda,h,w,\sigma_8,n_s)=(0.26,0.74,0.72,-1,0.8,0.96)$.
We fix the comoving size of the simulation box to $240\mathrm{Mpc}/h$,
and use $512^3$ particles, corresponding to a mass resolution of
$\approx 10^{10}M_\odot$.
%ZH: ``mass resolution'' here means DM particle mass ?

We assume a uniform galaxy distribution at a constant redshift $z_s=2$
(at which the simulation box has an angular size of $\theta_{\rm
  box}=3.5\mathrm{deg}$) and we discretize the mass distribution
between $z_s$ and the observer at $z=0$ with a sequence of 46 two
dimensional lenses of thickness $80\mathrm{Mpc}/h$. The surface
density on each lens plane is computed by projecting the
three--dimensional density measured from \texttt{Gadget2}
snapshots. We then apply the multi--lens--plane algorithm (see
\citep{RayTracingHartlap,RayTracingJain} for example) to trace the
deflections of $n_{ray}^2=2048^2$ light rays arranged on a square grid
of total size $\theta_{\rm box}$, from $z=0$ to $z_s$. Our
implementation of this algorithm is part of the \texttt{LensTools}
computing package we have been developing \citep{LensTools}, and have
released under the \texttt{MIT} license. Many different realizations
$r$ of the same shear field $\pmb{\gamma}_r(\pmb{\theta})$ can be
generated by picking different lens planes that lie between the
observer and $z_s$. The randomization procedure we adopt is the
following:
%ZH: we should cite some paper here. We didn't invent most of this
%procedure ourselves (except for maybe the 3-times thicker simulation
%output, and the random mixing of the planes from different N-body sims ?).

\begin{itemize}
\item For each lens-plane redshift $z_l$, select the snapshot at $z_l$ from the $i$--th $N$--body simulation, where $i$ is a random integer $i\in [1,N_s]$.
\item Choose randomly between the three orthogonal directions ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$: the lens plane will be perpendicular to this direction.
\item Choose the position of the plane along the snapshot: because the lens thickness is 1/3 the size of the box, we can cut three different slices of the simulation box for each orientation ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$. This gives a total of 9 choices for generating a lens plane out of a single $N$--body snapshot.
\item Perform a periodic random shift of the lens plane along its two directions.
%ZH: should we specify the range of the random shifts (0 to 1/2 the lens plane dimension?)
\item Repeat the above procedure for each lens-plane redshift $z_l$.
\end{itemize}  
%
This randomization procedure allows us to produce an (almost)
arbitrary number $N_r$ of shear realizations
$\pmb{\gamma}_r(\pmb{\theta})$. However, these realizations are not
guaranteed to be independent, if $N_s$ is not large enough. Using the
set of 200 independent $N$--body simulations, we construct different
ensembles with different choices of $N_s\in[1,200]$. Each of these
ensembles consists of the same number $N_r=1000$ of shear
realizations. We also build an additional ensemble with $N_s=1$ and
$N_r=10^5$ realizations. For each realization of each ensemble, we
reconstruct the convergence $\kappa_r(\pmb{\theta})$ 
%ZH: we should add 2 sentences on how you measured kappa.  Directly from the ray-tracing?
%   (but above, when you discuss ray-tracing, you mention only gamma).  Or did you do 
%    Kaiser-Squires on the gamma field ? 
and measure its
angular power spectrum $P^{\kappa\kappa}_r(l)$ defined as
\begin{equation}
\langle\tilde{\kappa}_r(\bb{l})\tilde{\kappa}_r(\bb{l}')\rangle = (2\pi)^2\delta_D(\bb{l}+\bb{l}')P^{\kappa\kappa}_r(l)
\end{equation}
%
As an additional summary statistic, we consider the counts of local
$\kappa$ maxima of a certain height $\kappa_0$, $n_r(\kappa_0)$
(hereafter \textit{peak counts}), with varying $\kappa_0$.
%ZH: state here the range and binning choice of $\kappa_0$
The fact that the ensemble of $N_r$ realizations is not completely
independent if $N_s$ is not large enough can have an effect on the
covariance estimators of both $P^{\kappa\kappa}$ and $n(\kappa_0)$.

%ZH: it would be logical to mention the other w,Sig,Om, sims here, and point to \ref{simtable})

\subsection{Cosmological parameter inference}
%

Let $\bbh{d}$ be a single estimate for a feature of dimension $N_b$, 
%ZH: ``Hat'' here refers to an estimator?
$\bb{d}(\bb{p})$ be the
%smooth expectation
%ZH: I believe ``smooth expectation'' means true mean value, yes?
true mean value of this feature at a point $\bb{p}$ in parameter space
(which has a dimension $N_p$) and $\bb{C}$ be the $N_b\times N_b$
feature covariance matrix. For the purpose of this work $\bb{p}$ is
the triplet $(\Omega_m,w,\sigma_8)$ and $\bb{d}$ is one of the
features -- either a power spectrum or a peak count -- in Table
\ref{featuretable}. While in many cases $\bb{d}(\bb{p})$ can be
predicted reasonably accurately by already existing emulators (see
\citep{coyote2,Nicaea} for example), the matter is more complicated
for covariance matrices.
%ZH: I am missing the point here.  Why is covariance matrix ``more complicated'' ?
%    Even to estimate a mean, one has to ``generate a series of mock realizations''.
%    Unless you are willing to equate a single realization as the mean.   But then
%    by the same logic, you could estimate the covariance matrix from two realizations.
%    Please clarify what you mean...  maybe I am missing something?  Or you simply mean
%    that published emulators usually do not emulate the cov.matrix (even though they could)?
%    Note that there is a paper by Schneider and Knox, in which they do an interpolation of the
%    power spectrum covariance matrix.
Estimating $\bb{C}$ from simulations involves generating a series of
mock realizations $\bbh{d}_r$ with $r=1...N_r$ and computing the
sample covariance $\bbh{C}$,

\begin{equation}
\bb{\bar{d}} = \frac{1}{N_r}\sum_{r=1}^{N_r} \bbh{d}_r,
\end{equation}

\begin{equation}
\label{covest}
\bbh{C} = \frac{1}{N_r-1}\sum_{r=1}^{N_r} (\bbh{d}_r - \bar{\bb{d}}) (\bbh{d}_r - \bar{\bb{d}})^T.
\end{equation}
%
Assuming a normal feature likelihood, together with a flat prior on
the parameter space, the parameter posterior distribution
$\mathcal{L}(\bb{p}\vert\bbh{d}_{\rm obs})$ given an observed instance of
$\bbh{d}$, which we call $\bbh{d}_{\rm obs}$, follows from Bayes' theorem,
%
\begin{equation}
\label{posteriorbayes}
-2\log\mathcal{L}(\bb{p}\vert\bbh{d}_{\rm obs}) = [\bbh{d}_{\rm obs}-\bb{d}(\bb{p})]^T\bbh{C}^{-1}[\bbh{d}_{\rm obs}-\bb{d}(\bb{p})].
\end{equation}
%
For the sake of simplicity, we approximate the posterior as a Gaussian
around its maximum. This corresponds to Taylor-expanding the simulated
feature to first order around a point $\bb{p}_0$ (ideally the maximum
of Eq.~\ref{posteriorbayes}):
%
\begin{equation}
\bb{d}(\bb{p}) \approx \bb{d}_0 + \bb{d}_0^\prime(\bb{p}-\bb{p}_0).
\end{equation}
%

To measure the derivatives of the features $\bb{d}'_0$ with respect to
the cosmological parameters, we make use of the public code
\texttt{NICAEA} \citep{Nicaea} for the power spectrum, and we use an
independent simulation set (containing simulations with a variety of
different combinations of $(\Omega_m,w,\sigma_8)$, see Table
\ref{simtable}) for the peak counts.

\begin{table}
\begin{center}
\begin{tabular}{c|c|c||c|c}
\toprule
$\Omega_m$ &  $w$ & $\sigma_8$ & $N_s$ & Number of $\kappa$ ensembles \\ \hline \hline
\midrule
%
0.26 & -1 & 0.8 & $1$ to $200$ & 16 \\
0.29 & -1 & 0.8 & 1 & 1 \\
0.26 & -0.8 & 0.8 & 1 & 1 \\
0.26 & -1 & 0.6 & 1 & 1 \\
%
\bottomrule
\end{tabular}
\end{center}
\caption{Summary of the shear ensembles used in this work.}
%ZH: So each of these have N_r=1000, yes?  You should state this here. And also,
%    Add the ensemble with N_s=1, N_r=10^5 to this table.
%    Also: point the reader to this table in the text, up front, when the 
%    ensembles are first discussed.
\label{simtable}
\end{table}

We can build the estimator for the posterior maximum $\bbh{p}$, given
the observation $\bbh{d}_{\rm obs}$, as follows:
%
\begin{equation}
\label{estimatormean}
\bbh{p} = \bb{p}_0 + \bbh{T}(\bbh{d}_{\rm obs}-\bb{d}_0),
\end{equation}

\begin{equation}
\bbh{T} = (\bb{d}_0'^T\bbh{C}^{-1}\bb{d}_0')^{-1}\bb{d}_0'^T\bbh{C}^{-1}.
\end{equation}
%
Because $\bbh{p}$ is estimated using a single noisy data instance
$\bbh{d}_{\rm obs}$, its estimate will be scattered around the true
value $\langle\bbh{p}\rangle_O$. In the following we use the
$\langle\rangle_O$ notation for expectation values taken with respect
to observations, while we keep the notation $\langle\rangle$ for
expectation values taken with respect to the simulations. Defining the
\textit{precision matrix} $\bbh{\Psi}=\bbh{C}^{-1}$, we can express
the estimator of the observational scatter in $\bbh{p}$:

\begin{equation}
\label{estimatorcovariance}
\h{\Sigma}_\bb{p} = \bbh{F}^{-1}\bb{d}_0'^T\bbh{\Psi}\langle(\bbh{d}_{\rm obs}-\bb{d}_0)(\bbh{d}_{\rm obs}-\bb{d}_0)^T\rangle_O\bbh{\Psi}\bb{d}_0'\bbh{F}^{-1},
\end{equation}

\begin{equation}
\label{estimatorfisher}
\bbh{F} = \bb{d}_0'^T\bbh{\Psi}\bb{d}_0'.
\end{equation}
%
Here we introduced the familiar Fisher matrix estimator $\bbh{F} =
\bb{d}_0'^T\bbh{\Psi}\bb{d}_0'$ and, for simplicity, we assumed
$\langle\bbh{d}_{\rm obs}\rangle_O=\bb{d}_0$, so that
$\langle(\bbh{d}_{\rm obs}-\bb{d}_0)(\bbh{d}_{\rm
  obs}-\bb{d}_0)^T\rangle_O=\bb{C}$.  When we perform an observation
$\bbh{d}_{\rm obs}$, the parameter estimate $\bbh{p}$ is a random draw
from a probability distribution with variance $\h{\Sigma}_\bb{p}$,
which inherits noise from the simulations. The noise in the covariance
estimator (Eq.~\ref{covest}) and in its inverse $\bbh{\Psi}$ propagate
all the way to the posterior (Eq.~\ref{posteriorbayes}), the parameter
estimate (Eq.~\ref{estimatormean}) and its variance
(Eq.~\ref{estimatorcovariance}). Following
refs.~\citep{DodelsonSchneider13,Taylor12,MasumotoWishart} we compute
the expectation value of Eq.~(\ref{estimatorcovariance}) over
simulations, $\langle\h{\Sigma}_\bb{p}\rangle$, up to $O(1/N_r^2)$ by
expanding Eq.~(\ref{estimatorcovariance}) to quartic order in the
statistical fluctuations of $\bbh{\Psi}$. Denoting the noiseless
parameter covariance, i.e. the usual Fisher matrix, as
$\Sigma_\bb{p}=\bb{F}^{-1}$, we find the result~\footnote{The
  details of the calculation are given in Appendix A.}:

\begin{widetext}
\begin{equation}
\label{quarticdegradation}
\langle\h{\Sigma}_\bb{p}\rangle = \Sigma_\bb{p}\left[1+\frac{N_b-N_p}{N_r}+\frac{(N_b-N_p)(N_b-N_p+2)}{N_r^2}\right] + O\left(\frac{1}{N_r^3}\right).
\end{equation}
\end{widetext}
%
Next, we restrict ourselves to the large $N_r$ limit, and we further
investigate the behavior of the $O(1/N_r)$ term. We consider three
cases \footnote{The details of these calculations are given in
  Appendix B}:

\begin{enumerate}
\item If the true data covariance $\bb{C}$ is known, the estimator in
  Eq.~(\ref{estimatorcovariance}) is biased, and the dominant
  contribution of the bias comes from the second order fluctuations in
  $\bbh{\Psi}$. Once the expectation values over simulations are
  taken, the bias sums up to

\begin{equation}
\label{dodelsonscaling}
\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}\left(1+\frac{N_b-N_p}{N_r}\right).
\end{equation}
%
This is the result obtained by ref.~\citep{DodelsonSchneider13}.

\item Usually the true data covariance is unknown, and it is tempting
  to plug in its estimator $\bbh{C}$, measured from the same
  simulation set we use to compute $\bbh{\Psi}$. This approach has
  been used before in the literature
  (e.g.~\citep{MinkPetri,MinkShirasaki}). If this is done without
  correcting for the bias in $\bbh{\Psi}$ (see Eq.~\ref{firstmoment}
  below), 
%ZH: we should probably cite Hartlap et al. and Taylor et al. here for this Psi bias.  (I assume this is what you mean in eq. 19)
  the parameter variance will have a contribution from both the second
  and first-order fluctuations in $\bbh{\Psi}$, which now have a
  nonzero expectation value. In this case the bias sums up to
%
\begin{equation}
\label{mockscalinguncorrected}
\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}\left(1-\frac{N_b-N_p}{N_r}\right).
\end{equation}

@@

\section{Conclusions}
